---
title: ' Relationship between forearm length and height (.)'
author: "HS2440 (.)"
date: "September 26, 2020 (.)"
output:
  html_document: default
  pdf_document: default
---

## I. Introduction 

Parts marked with (.) need updating. 
Part 1 (.)

This assignment is about using 10 randomly selected data 
points from the given sample a20a1data.csv to determine 
whether there is a relationship between forearm length 
and height.

The sample data was collected by using rulers to measure 
out the forearm length and height of the participants in
centimeters.

I choose forearm length to be the response variable as it
tends to vary with height.
I choose height to be the explanatory variable since it 
explains changes and affects our response variable forearm 
length.

## II. Exploratory Data Analysis
The integers below are the IDs of the 10 randomly chosen 
observations by using the sample( ) function, these 10 
observations are used as the sample data in this assignment.
```{r,echo=FALSE}
set.seed(2440)
sample(346,size=10)
random_sample_hs<- data.frame(height = c(189, 174, 171, 166, 180, 175, 160, 167, 175, 175), forearm = c(31.5, 22, 23, 17, 25, 27, 22, 22, 22, 29))
boxplot(random_sample_hs$height, main="Boxplot of heights in cm from random_sample_hs #2440")
boxplot(random_sample_hs$forearm, main="Boxplot of forearm lengths in cm from random_sample_hs #2440")
plot(random_sample_hs$height, random_sample_hs$forearm, main="Scatterplot of random_sample_hs #2440", xlab="heights of participants (cm)", ylab="forearm length of participants (cm)" )

```

Part 2 (.)
The random_sample_hs data is the set containing 10 randomly
chosen data points from the "a20a1data" dataset.

The distribution of the response variable is right-skewed 
rather than being normal.

The explanatory variable height has a center of 174.5,
a range of 29 cm, a variance of 64.0 and an outlier at 
189 cm.
The response variable forearm length has a center of 22.5,
a range of 14.5, a variance of 17.5 and no outliers.

## III. Methods and Model

Part 3 (.)
```{r,echo=FALSE}
lmod=lm(random_sample_hs$forearm~random_sample_hs$height)
summary(lmod)
plot(random_sample_hs$height, random_sample_hs$forearm, main="Scatterplot with linear regression model #2440", xlab="heights of participants (cm)", ylab="forearm length of participants (cm)" )
abline(lmod)
```

This linear regression model is produced by using forearm
as y and heights as x. We acquired that this model has an
intercept (B0) of -43.9 and a slope (B1) of 0.39. Hence 
the regression parameters are not zero.

The estimates of the regression parameters show that
there is a positive correlation between heights 
and forearm lengths.The mean of forearm length increases by
0.39 cm whenever there is a 1 cm increase in height.

Additionally, the p-value of our independent variable is
0.0123, which is less than the benchmark significance level 
of 0.05. Thus the sample data provides enough evidence to 
reject the null hypothesis that height has no correlation 
with forearm length.
In other words, the sample data favors the hypothesis that
there is a non-zero correlation between height and forearm
length.

## IV. Discussions and Limitations

Part 4 (.)

A lurking variable can be whether a person regularly does 
exercises involving the usage of forearm.
One limitation of our fit is the relatively small sample 
size. With a bigger sample size, the data can represent 
the relationship between forearm length and height better.
In addition, we also assumed their relationship is linear.

Example of another pair of variables that we can use SLR 
on is "Amount of alcohol consumed and blood alcohol content",
where blood alcohol content is the response variable.